results

### 2024-02-16 reproduce-results.qmd
cleaning up and documenting summary functions

---
title: "results"
format: html
---

@@

This quarto document reproduces the results section in Nascimento de Lima et al. (2024). *The value of environmental surveillance for pandemic response*.

>>>>

---
title: "results"
format: html
author: "Pedro Nascimento de Lima"
---

@@

This quarto document reproduces the results section in Nascimento de Lima et al. (2024). *The value of environmental surveillance for pandemic response*. For details on how to install dependencies, and reproduce these results, see the `README.md` file.

# Run Results

First, we instantiate the model and run it over the experimental designs used in the paper.

```{r}
# Source all dependencies and model scripts
source("./R/library.R")

# Single run examples -----------------------------------------------------
model <- OdinMetapop$new("stochastic_metapopulation.R", s$data_file)

# Verify that model runs with base-case parameters, no NPIs

# Set NPI case threshold to 1000 (i.e., do not introduce NPIs)
model$set_input(name = "c", value = Inf)
test_results <- model$simulate()

# The res_long data.frame contains jurisdiction-day-replication-level results

head(model$res_long)
```
